---
title: "DATA_607_Project_2"
author: "Md Jalal Uddin"
date: "October 9, 2016"
output: pdf_document
---


DATA Set 1:

```{r}
# Load packages 

library(dplyr)
library(tidyr)
library(stringr)
library(knitr)
library(ggplot2)


```


```{r}
BPL_Data <- read.csv("C:/Users/sql_ent_svc/Google Drive/DATA_607/Project_2/BPL.csv", header = TRUE,  stringsAsFactors = FALSE )
head(BPL_Data)

#data Source:http://www.espncricinfo.com/bangladesh-premier-league-2015-16/engine/series/921139.html?view=pointstable

```

Rearrange the data with new column name using select statement
```{r}
BPL_Data1<- BPL_Data %>%
select(Teams,Match, Won, PTS, For, Against) %>%
rename(BPL_Teams = Teams, Match_Played=Match, Match_Won = Won, Total_Points = PTS, Own_score = For, score_Against= Against)
BPL_Data1

```

By using select statement again I am selecting the only those variable whose we need for my analysis
```{r}
BPL_Score_Points <- BPL_Data1%>%
select(BPL_Teams, Match_Won, Own_score, score_Against)
BPL_Score_Points

```

Selecting only 3 variable
```{r}
BPL_Score_Points1 <- BPL_Score_Points%>%
select(BPL_Teams, Own_score, score_Against)
BPL_Score_Points1

```
 
 finding summary of BPL_Score_Points1 data
 
```{r}
summary(BPL_Score_Points1)
```


Rearrange data using gather statement
```{r}
BPL_Score_Points3 <- gather(BPL_Score_Points1, "Team_Score_Types","Scores", 2:3)
BPL_Score_Points3

```

Creating a geomatric bar plot by using ggplot
```{r}
ggplot(data = BPL_Score_Points3, aes(x = BPL_Teams, y = Scores, fill = Team_Score_Types))+ geom_bar(stat="identity", position="dodge") + ggtitle("Team score for own and against") + ylab("scores") + coord_flip()

#source: http://docs.ggplot2.org/0.9.3.1/geom_bar.html

```


DATA Set 2:

```{r}
Animal_Data <- read.csv("C:/Users/sql_ent_svc/Google Drive/DATA_607/Project_2/Animal_Sleep.csv", header = TRUE, sep = "\t", stringsAsFactors = TRUE )
head(Animal_Data)

#data Source:http://www.statsci.org/data/general/sleep.txt

```

Rearrange the data by using select statement
```{r}
Animal_Data1 <- Animal_Data%>%
select(Species, BodyWt, BrainWt, TotalSleep,LifeSpan, Danger)
head(Animal_Data1)

```

we can find mean of a specific variable or column by using followoing mean function
```{r}
mean(Animal_Data1$BodyWt)

```

Finding correlation of different variables 
```{r}
(Cor.BodyWt_BrainWt <- cor.test( Animal_Data1$BodyWt,Animal_Data1$BrainWt))
(Cor.BodyWt_LifeSpan <- cor.test( Animal_Data1$BodyWt,Animal_Data1$LifeSpan))
(Cor.TotalSleep_BrainWt <- cor.test( Animal_Data1$TotalSleep,Animal_Data1$BrainWt))
(Cor.LifeSpan_BrainWt <- cor.test( Animal_Data1$LifeSpan,Animal_Data1$BrainWt))

```

Here we can see variables Bodywt and BrainWt have very strong positive relationship by seeing the correlation coefficient between them. 

Finding Regression by using following statement
```{r}
Reg_BodyWt_BrainWt <- lm(BodyWt~BrainWt+LifeSpan+Danger, data=Animal_Data1)
summary(Reg_BodyWt_BrainWt)

```

Rearrange data selecting only 3 variable for my analysis
```{r}
Animal_Data2 <- Animal_Data1%>%
select(Species, BodyWt, BrainWt)
head(Animal_Data2)
```

rearange data using gather function
```{r}
Animal_Data3 <- gather(Animal_Data2, "weight_Types","weight", 2:3)
head(Animal_Data3)


```


finding the geomatric bar plot using ggplot
```{r}
ggplot(data = Animal_Data3, aes(x = Species, y = weight, fill = weight_Types))+ geom_bar(stat="identity", position="dodge") + ggtitle("Body and brain weight for different Species") + ylab("weight") + coord_flip()

```



DATA SEt 3:

```{r}
Pima_Indian_Data <- read.csv("C:/Users/sql_ent_svc/Google Drive/DATA_607/Project_2/Pima_Indian_diabetes_data_set.csv", header = FALSE, sep = "," , stringsAsFactors = FALSE)
head(Pima_Indian_Data)

#data Source: http://archive.ics.uci.edu/ml/datasets/Pima+Indians+Diabetes


```

Rearrange the data set by changing the variable name/column name by folloing statement

```{r}
names(Pima_Indian_Data)[names(Pima_Indian_Data) == "V1"] <- "Number_of_Times_Pregnant" 
names(Pima_Indian_Data)[names(Pima_Indian_Data) == "V2"] <- "Plasma_glucose" 
names(Pima_Indian_Data)[names(Pima_Indian_Data) == "V3"] <- "Diastolic_Pressure" 
names(Pima_Indian_Data)[names(Pima_Indian_Data) == "V4"] <- "Triceps_skin_thickness" 
names(Pima_Indian_Data)[names(Pima_Indian_Data) == "V5"] <- "Serum_insulin" 
names(Pima_Indian_Data)[names(Pima_Indian_Data) == "V6"] <- "BMI" 
names(Pima_Indian_Data)[names(Pima_Indian_Data) == "V7"] <- "Pedigree_function" 
names(Pima_Indian_Data)[names(Pima_Indian_Data) == "V8"] <- "Age" 
names(Pima_Indian_Data)[names(Pima_Indian_Data) == "V9"] <- "Class_variable" 

head(Pima_Indian_Data)

```


Arranging the data to see who has hightest BMI

```{r}
Pima_Indian_Data1 <- Pima_Indian_Data %>% 
           select(Number_of_Times_Pregnant,Plasma_glucose, Diastolic_Pressure, BMI, Age) 

head(Pima_Indian_Data1)


```

Finding the correlation between different variables

```{r}

(Cor.BMI_Age <- cor.test( Pima_Indian_Data1$BMI,Pima_Indian_Data1$Age))
(Cor.BMI_Diastolic_Pressure <- cor.test( Pima_Indian_Data1$BMI,Pima_Indian_Data1$Diastolic_Pressure))
(Cor.Age_Diastolic_Pressure <- cor.test( Pima_Indian_Data1$Age,Pima_Indian_Data1$Diastolic_Pressure))
(Cor.Age_Diastolic_Plasma_glucose <- cor.test( Pima_Indian_Data1$Plasma_glucose ,Pima_Indian_Data1$Diastolic_Pressure))
(Cor.BMI_Plasma_glucose <- cor.test( Pima_Indian_Data1$BMI,Pima_Indian_Data1$Plasma_glucose))

```

finding Regression 
```{r}
Reg_Plasma_glucose <- lm(Plasma_glucose~Diastolic_Pressure+Age+BMI, data=Pima_Indian_Data1)
summary(Reg_Plasma_glucose)

```

Selecting only 3 variables for my analysis

```{r}
Pima_Indian_Data2 <- Pima_Indian_Data1%>%
select(Number_of_Times_Pregnant, Diastolic_Pressure, BMI)
head(Pima_Indian_Data2)


```

rearrange data using gather function
```{r}
Pima_Indian_Data3 <- gather(Pima_Indian_Data2, "pressure_BMI","pressure", 2:3)
head(Pima_Indian_Data3)

```

finding geomaric bar plot using ggplot
```{r}
ggplot(data = Pima_Indian_Data3, aes(x = Number_of_Times_Pregnant, y = pressure, fill =  pressure_BMI))+ geom_bar(stat="identity", position="dodge") + ggtitle("Pregnancy, pressure and BMI") + ylab("Pressure") + coord_flip()


```



